---
title: "Teen Smartphone Usage and Addiction Impact Dataset"
author: "Aleksandra Dobosz, Aleksandra Engel, Adam Gonet, Kamil Laskowski"
date: "2026-05-04"
output: 
  html_document:
    code_folding: show
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 6
    number_sections: false
    theme: flatly
  pdf_document:
    toc: true
    toc_depth: '5'
    highlight: espresso
editor_options: 
  markdown: 
    wrap: 72
---

# Teen Smartphone Usage and Addiction Impact Dataset

## About the Dataset

This dataset, sourced from Kaggle, focuses on understanding **smartphone
usage patterns among teenagers** and the impact of excessive phone use
on their **academic performance, mental health, and daily lifestyle**.
With the rapid increase in smartphone dependency among adolescents, it
has become important to study how usage habits influence well-being and
performance.

The dataset captures multiple aspects of teenage behavior, including
**addiction levels, time distribution across activities, sleep patterns,
social interactions, and mental health indicators**. From our
perspective, we aim to build regression models to examine which factors
have the greatest impact on smartphone addiction levels.

------------------------------------------------------------------------

## Column Descriptions

Demographic Information 

- **ID**: Unique identifier for each student\
- **Name**: Name of the student\
- **Age**: Age of the teenager\
- **Gender**: Gender of the student\
- **Location**: Geographic location\
- **School_Grade**: Current academic or level

Smartphone Usage & Time Distribution 

- **Daily_Usage_Hours**: Average smartphone usage per day (hours)\
- **Weekend_Usage_Hours**: Average smartphone usage on weekends\
- **Screen_Time_Before_Bed**: Screen time before going to sleep\
- **Phone_Checks_Per_Day**: Number of times the phone is checked daily\
- **Apps_Used_Daily**: Number of apps used per day

Activity-Based Usage 

- **Time_on_Social_Media**: Hours spent on social media platforms\
- **Time_on_Gaming**: Hours spent on mobile gaming\
- **Time_on_Education**: Hours spent on educational activities\
- **Phone_Usage_Purpose**: Primary purpose of smartphone usage

Health & Lifestyle Indicators 

- **Sleep_Hours**: Average hours of sleep per day\
- **Exercise_Hours**: Time spent on physical exercise\
- **Anxiety_Level**: Indicator of anxiety level\
- **Depression_Level**: Indicator of depression level\
- **Self_Esteem**: Self-esteem score

Social & Family Factors 

- **Social_Interactions**: Level of in-person social interaction\
- **Family_Communication**: Quality or frequency of communication with family\
- **Parental_Control**: Level of parental monitoring or restrictions

Outcome Variables 

- **Academic_Performance**: Indicator of academic performance\
- **Addiction_Level**: Level of smartphone addiction (target variable)

------------------------------------------------------------------------

## Problem Description

Smartphone use has become an essential part of teenagers’ daily lives,
but excessive usage may lead to addiction and negatively affect mental
health, sleep patterns, social interactions, and academic performance.
Smartphone addiction among adolescents is an increasingly important
social and psychological issue. The goal of this project is to use
regression analysis to identify which behavioral, lifestyle, and
psychological factors most strongly influence the level of smartphone
addiction. Understanding these relationships can support early
intervention and promote healthier smartphone usage habits among
teenagers.

------------------------------------------------------------------------

# Importing neccessary libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(dplyr)
library(readr)
library(caret)
library(reshape2)
library(ggplot2)
library(e1071)
library(gridExtra)
library(patchwork)
library(googledrive)

if (!requireNamespace("googledrive", quietly = TRUE)) {install.packages("googledrive")}
if (!requireNamespace("dplyr", quietly = TRUE)) install.packages("dplyr")
if (!requireNamespace("ggplot2", quietly = TRUE)) install.packages("ggplot2")

library(dplyr)
library(ggplot2)

```

```{r download data from google drive}
#path to google file with data 
file_id <- "1mJ-iLbHWiaPLHltrnIwjfNcbtW_4u8fd"
url <- paste0("https://drive.google.com/uc?export=download&id=", file_id)
df <- read.csv(url)
```

# Section 1: Data Loading and Initial Exploration

In this section, we load the dataset and perform initial exploratory
analysis to understand the data structure, identify potential issues,
and assess data quality.

```{r info}
# Print dataset dimensions (rows and columns)
cat("Dataset shape:", dim(df), "\n")

# Display first few rows of the dataset
head(df)
```

```{r summary}
# Descriptive statistics of the dataset
summary(df)

# Count duplicated rows in the dataset
sum(duplicated(df))

# Count missing values in each column
colSums(is.na(df))
```

Now as we have don't have missing values, we are going to remove
unnecessary columns and test-train split.

# Section 2: Data Cleaning and Preprocessing

Now we'll remove unnecessary columns and split the data into training
and test sets. Then, we'll apply one-hot encoding to categorical
variables.

### Step 1: Remove non-informative columns

Columns like 'Name' and 'ID' don't contribute to predictions since they
are just identifiers. We'll drop them to reduce noise.

```{r remove columns}
# Remove selected columns using dplyr
df <- df %>% select(-Name, -ID)
```

### Step 2: Train-Test Split

We split the data into 80% training and 20% testing sets. Using
random_state=123, which ensures reproducibility.

```{r train test split}
set.seed(123)

index <- createDataPartition(df[[1]], p = 0.8, list = FALSE)

df_train <- df[index, ]
df_test  <- df[-index, ]

# Display training set
head(df_train)
cat("SHAPE:", dim(df_train), "\n")

# Display test set
head(df_test)
cat("SHAPE:", dim(df_test), "\n")
```

### Step 3: Analyze data types and cardinality

Let's examine the data types and unique values for each column to
identify categorical variables that need encoding.

```{r data structure}
# Structure of dataset
glimpse(df_train)

# Unique values
unique(df_train$School_Grade)
unique(df_train$Gender)

# Count unique values
n_distinct(df_train$Location)

# Remove column
df_train <- df_train %>% select(-Location)

# Unique values
unique(df_train$Phone_Usage_Purpose)
```

Based on the above analysis, we need to apply one-hot encoding to
School_Grade, Gender and Phone_Usage_Purpose

# Section 3: Exploratory Data Analysis

This section analyzes relationships between variables, target variable
distribution, and statistical significance tests.

```{r correlations}
#only numeric columns
numeric_df <- df_train[sapply(df_train, is.numeric)]

#calculate Kendall correlation matrix, because it's robust to non-normal distributions
corr <- cor(numeric_df, method = "kendall", use = "complete.obs")

#print correlation matrix
corr

#convert correlation matrix to long format
corr_melt <- melt(corr)

#heatmap
ggplot(corr_melt, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c() +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  labs(
    title = "Kendall Correlation Heatmap",
    x = "",
    y = ""
  )
```

-   \< 0.2 – no linear correlation
-   0.2 – 0.4 – low linear correlation
-   0.4 -0.7 – mid linear correlation
-   0.7 – 0.9 – strong linear correlation
-   \> 0.9 – very strong linear correlation

Correlation analysis shows that addiction level is most strongly
associated with usage-intensity features, especially Daily_Usage_Hours,
as well as Apps_Used_Daily, Time_on_Social_Media, Phone_Checks_Per_Day
and Time_on_Gaming. A negative correlation with Sleep_Hours suggests
that higher addiction levels are linked to reduced sleep, while most
other variables show only weak relationships.

### Dependent Variable Analysis

```{r target distribution}
#summary statistics for target variable
cat("Addiction_Level Statistics:\n")

cat(" Mean:", mean(df_train$Addiction_Level, na.rm = TRUE), "\n")
cat(" Median:", median(df_train$Addiction_Level, na.rm = TRUE), "\n")
cat(" Std Dev:", sd(df_train$Addiction_Level, na.rm = TRUE), "\n")
cat(" Min:", min(df_train$Addiction_Level, na.rm = TRUE), "\n")
cat(" Max:", max(df_train$Addiction_Level, na.rm = TRUE), "\n")
cat(" Skewness:", skewness(df_train$Addiction_Level, na.rm = TRUE), "\n")
cat(" Kurtosis:", kurtosis(df_train$Addiction_Level, na.rm = TRUE), "\n")

#histogram of target variable
ggplot(df_train, aes(x = Addiction_Level)) +
  geom_histogram(bins = 30, fill = "#21918c", color = "#21918c") +
  labs(
    title = "Histogram - Addiction_Level",
    x = "Addiction Level",
    y = "Frequency"
  ) +
  theme_minimal()

#skewness of target variable
skewness(df_train$Addiction_Level, na.rm = TRUE)
```

Let's try log and square root transformations to improve normality

```{r transformations}
# Histogram - original data
p1 <- ggplot(df_train, aes(x = Addiction_Level)) +
  geom_histogram(bins = 30, fill = "#21918c", color = "#21918c") +
  labs(title = "Histogram - Addiction_Level") +
  theme_minimal(base_size = 12)

# Histogram - log transformed
p2 <- ggplot(df_train, aes(x = log(Addiction_Level))) +
  geom_histogram(bins = 30, fill = "#21918c", color = "#21918c") +
  labs(title = "Histogram - log(Addiction_Level)") +
  theme_minimal(base_size = 12)

# Arrange plots side by side
grid.arrange(p1, p2, ncol = 2)
```

Log scaling doesn't improve the distribution of target variable - let's
try square root.

```{r transformations2}
# Histogram - original data
p1 <- ggplot(df_train, aes(x = Addiction_Level)) +
  geom_histogram(bins = 30, fill = "#21918c", color = "#21918c") +
  labs(title = "Histogram - Addiction_Level") +
  theme_minimal(base_size = 12)

# Histogram - sqrt transformed data
p2 <- ggplot(df_train, aes(x = sqrt(Addiction_Level))) +
  geom_histogram(bins = 30, fill = "#21918c", color = "#21918c") +
  labs(title = "Histogram - sqrt(Addiction_Level)") +
  theme_minimal(base_size = 12)

# Arrange plots side by side
grid.arrange(p1, p2, ncol = 2)
```

```{r stats 2}
# Original data
skew_original <- skewness(df_train$Addiction_Level, na.rm = TRUE)
kurt_original <- kurtosis(df_train$Addiction_Level, na.rm = TRUE)

# Square root transformation
skew_sqrt <- skewness(sqrt(df_train$Addiction_Level), na.rm = TRUE)
kurt_sqrt <- kurtosis(sqrt(df_train$Addiction_Level), na.rm = TRUE)

# Log transformation
skew_log <- skewness(log(df_train$Addiction_Level), na.rm = TRUE)
kurt_log <- kurtosis(log(df_train$Addiction_Level), na.rm = TRUE)

# Print results
cat("Original:\n")
cat(" Skewness:", skew_original, "\n")
cat(" Kurtosis:", kurt_original, "\n\n")

cat("Sqrt transformed:\n")
cat(" Skewness:", skew_sqrt, "\n")
cat(" Kurtosis:", kurt_sqrt, "\n\n")

cat("Log transformed:\n")
cat(" Skewness:", skew_log, "\n")
cat(" Kurtosis:", kurt_log, "\n")
```

The target variable Addiction_Level will be modeled in its original
scale. Applied transformations such as square root and logarithm
increased skewness and kurtosis and even less normal distribution. Since
most machine learning models do not require the target variable to
follow a normal distribution, keeping the original form is the most
appropriate choice.

### Statistical Analysis

```{r violin}
# Violin plot: distribution by school grade
ggplot(df_train, aes(x = School_Grade, y = Addiction_Level)) +
  geom_violin(fill = "#7ad151", color = "#7ad151") +
  geom_boxplot(width = 0.1, outlier.size = 1, alpha = 0.2) +
  labs(title = "Distribution of Addiction_Level by school grade") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

# Perform Kruskal-Wallis test
kruskal_result <- kruskal.test(Addiction_Level ~ School_Grade, data = df_train)

# Print p-value
cat(sprintf("Kruskal-Wallis p-value = %.5f\n", kruskal_result$p.value))
```

To statistically verify the visual differences observed in the violin
plot, we applied Kruskal–Wallis. This non-parametric test was chosen due
to the non-normal distribution of the target variable and the presence
of multiple groups. The results indicate that there is no significant
difference between addiction level across school grades.

```{r barplot}
# Barplot: mean Addiction_Level by Gender with SD error bars
ggplot(df_train, aes(x = Gender, y = Addiction_Level)) +
  stat_summary(fun = mean, geom = "bar", fill = "#fde725") +
  stat_summary(fun.data = mean_sdl, geom = "errorbar", width = 0.2) +
  labs(
    title = "Addiction Level by Gender",
    x = "Gender",
    y = "Addiction_Level"
  ) +
  theme_minimal(base_size = 12)
```

Addiction level seems to be consistent across all genders - there are no
significant differences based on the plot output.

```{r histogram}
# Histogram with density curve (KDE equivalent)
ggplot(df_train, aes(x = Daily_Usage_Hours)) +
  geom_histogram(aes(y = ..density..), bins = 20, fill = "#fde725", color = "yellow") +
  geom_density(color = "#440154", linewidth = 1) +
  labs(
    title = "Distribution of Daily Screen Time",
    x = "Daily Usage Hours",
    y = "Density"
  ) +
  theme_minimal(base_size = 12)
```

The plot shows that most people spend around 4 to 6 hours per day using
screens. The highest frequency is in this range, while very low and very
high screen time values occur less often. Overall, daily screen time is
concentrated around moderate usage levels, with only a few users
spending more than 8 hours per day.

```{r violin2}
# Violin plot of Addiction_Level by Age
ggplot(df_train, aes(x = factor(Age), y = Addiction_Level, fill = factor(Age))) +
  geom_violin(color = "black") +
  geom_boxplot(width = 0.1, alpha = 0.4) +
  scale_fill_viridis_d() +
  labs(title = "Distribution of Addiction_Level by age") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90))
```

Addiction level seems to be consistent across all age groups - there are
no significant differences based on the plot output.

```{r by age}
# Group by Age and compute mean Family_Communication
grouped_df <- df_train %>%
  group_by(Age) %>%
  summarise(Family_Communication = mean(Family_Communication, na.rm = TRUE))

# Line plot
ggplot(grouped_df, aes(x = Age, y = Family_Communication)) +
  geom_line(color = "#2a788e") +
  geom_point(color = "#2a788e") +
  scale_x_continuous(breaks = seq(min(grouped_df$Age), max(grouped_df$Age), by = 1)) +
  labs(
    title = "Line Plot: Age vs Family Communication",
    x = "Age",
    y = "Average Family Communication Score"
  ) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.minor = element_blank())
```

The line plot shows how average family communication changes with age.
The score increases slightly from age 13 to 16 and reaches its highest
value at age 17. After that, it decreases for ages 18 and 19. Overall,
family communication appears relatively stable across ages, with a small
peak in mid-to-late adolescence.

```{r plot 2}
# Group by Age and compute mean Depression_Level
grouped_df <- df_train %>%
  group_by(Age) %>%
  summarise(Depression_Level = mean(Depression_Level, na.rm = TRUE))

# Line plot with x-axis ticks every 1 unit
ggplot(grouped_df, aes(x = Age, y = Depression_Level)) +
  geom_line(color = "#22a884") +
  geom_point(color = "#22a884") +
  scale_x_continuous(breaks = seq(min(grouped_df$Age), max(grouped_df$Age), by = 1)) +
  labs(
    title = "Line Plot: Age vs Depression Level",
    x = "Age",
    y = "Average Depression Level"
  ) +
  theme_minimal(base_size = 12)
```

Based on the plot, depression levels appear to increase between ages 13
and 15, followed by a decline at age 16. Afterward, there is a rise in
depression levels up to age 18, which then decreases at age 19

```{r plot 3}
# Filter dataset for specific usage hours
usage_hour <- 5
filtered_df <- df_train %>%
  filter(Daily_Usage_Hours == usage_hour)

# Count categories
purpose_counts <- filtered_df %>%
  count(Phone_Usage_Purpose)

# Pie chart
ggplot(purpose_counts, aes(x = "", y = n, fill = Phone_Usage_Purpose)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  scale_fill_viridis_d()+
  labs(
    title = paste("Phone Usage Purpose Distribution for", usage_hour, "Daily Usage Hours"),
    x = "",
    y = ""
  ) +
  theme_void() +
  theme(legend.title = element_blank())
```

The chart shows how students use their phones in a day, with 30.4% spent
on social media, 25.0% on other activities, and 23.2% on education.
Browsing takes up 14.3%, and gaming is the least at 7.1%. Social media
is the most popular activity, followed by educational use.

```{r plot 4}
# Group by Exercise_Hours and compute mean Addiction_Level
grouped_df <- df_train %>%
  group_by(Exercise_Hours) %>%
  summarise(Addiction_Level = mean(Addiction_Level, na.rm = TRUE))

# Line plot
ggplot(grouped_df, aes(x = Exercise_Hours, y = Addiction_Level)) +
  geom_line(color = "#414487") +
  geom_point(color = "#414487") +
  labs(
    title = "Line Plot: Exercise Hours vs Addiction Level",
    x = "Exercise Hours",
    y = "Average Addiction Level"
  ) +
  theme_minimal(base_size = 14) +
  theme(panel.grid.minor = element_blank())
```

The line graph shows the relationship between exercise hours and
addiction level. When exercise hours are low, the addiction level stays
high (around 9). As exercise hours increase, the addiction level
generally goes down, showing that exercising more may help reduce
addiction. However, the graph has a few sudden spikes and drops, which
means the trend is not perfectly smooth.

```{r plot 5}
# Group by Time_on_Social_Media and compute mean Academic_Performance
grouped_df <- df_train %>%
  group_by(Time_on_Social_Media) %>%
  summarise(Academic_Performance = mean(Academic_Performance, na.rm = TRUE))

# Line plot
ggplot(grouped_df, aes(x = Time_on_Social_Media, y = Academic_Performance)) +
  geom_line(color = "#7ad151") +
  geom_point(color = "#7ad151") +
  labs(
    title = "Time on Social Media vs Academic Performance",
    x = "Time on Social Media (hours)",
    y = "Average Academic Performance"
  ) +
  theme_minimal(base_size = 14) +
  theme(panel.grid.minor = element_blank())
```

This graph suggests that time on social media doesn’t have a clear or
consistent impact on academic performance. The relationship seems to be
more unpredictable, with academic performance fluctuating regardless of
social media use.

```{r plot 6}
ggplot(df_train, aes(x = factor(Parental_Control), y = Addiction_Level)) +
  geom_violin(fill = "#1fa187", color = "#1fa187") +
  geom_boxplot(width = 0.1, alpha = 0.4) +
  labs(
    title = "Distribution of Addiction_Level by Parental Control",
    x = "Parental Control",
    y = "Addiction Level"
  ) +
  theme_minimal()
```

Addiction level seems to be consistent across both groups - there are no
significant differences based on the plot output.

```{r plot 7}
#numeric columns selection
num_df <- df_train %>% select(where(is.numeric))

#plots
plot_list <- lapply(names(num_df), function(col) {
  ggplot(num_df, aes(x = .data[[col]])) +
    geom_histogram(bins = 20, fill = "#b5de2b", color = "#b5de2b") +
    labs(title = col) +
    theme_minimal(base_size = 6)
})

#combine plots
wrap_plots(plot_list)
```

# Section 4: Feature Engineering

We'll create derived features to capture behavioral patterns, reduce
dimensionality, and improve model performance.

### One-hot-encoding on Gender, School_Grade & Phone_Usage_Purpose

```{r one-hot encoding1}

df_train_encoded <- model.matrix(~ Gender + School_Grade + Phone_Usage_Purpose, data = df_train) |> as.data.frame()

df_train_encoded <- df_train_encoded[, !names(df_train_encoded) %in% "(Intercept)"]

#keeping only encoded
df_train <- cbind(df_train[, !names(df_train) %in% c("Gender", "School_Grade", "Phone_Usage_Purpose")],
            df_train_encoded)

str(df_train)

```

### Additional features

We created additional features to better capture behavioral patterns
related to smartphone usage, including usage intensity, night-time
activity, and lifestyle balance.

-   **Total_Phone_Time** – total daily time spent on the phone, calculated
    as the sum of social media, gaming, and educational usage. It
    represents overall smartphone exposure.
-   **Checks_per_Hour** – the number of phone checks normalized by daily
    usage hours, capturing compulsive checking behavior rather than long
    continuous sessions.
-   **Night_Usage_Ratio** – the proportion of total phone usage that occurs
    before bedtime, reflecting potentially unhealthy night-time usage
    patterns.
-   **Digital_Life_Balance** – a ratio combining sleep and physical activity
    relative to phone usage, indicating the balance between offline
    lifestyle and digital behavior.
-   **Entertainment_to_Education_Ratio** – the relationship between
    entertainment-related phone use (social media and gaming) and
    educational use, distinguishing productive from leisure-oriented
    behavior.
-   **Exercise_Level** – a categorical variable derived from weekly exercise
    hours, grouping physical activity into very low, low, moderate, and
    high levels to improve interpretability.
    
```{r new features}
df_train$Total_Phone_Time <- df_train$Time_on_Social_Media + df_train$Time_on_Gaming + df_train$Time_on_Education
df_train$Checks_per_Hour <- df_train$Phone_Checks_Per_Day / (df_train$Daily_Usage_Hours + 1e-12)
df_train$Night_Usage_Ratio <- df_train$Screen_Time_Before_Bed / (df_train$Daily_Usage_Hours + 1e-12)
df_train$Digital_Life_Balance <- (df_train$Exercise_Hours + df_train$Sleep_Hours) / (df_train$Daily_Usage_Hours + 1e-12)

df_train$Entertainment_to_Education_Ratio <-(df_train$Time_on_Social_Media + df_train$Time_on_Gaming) / (df_train$Time_on_Education + 1e-12)

df_train$Exercise_Level <- cut(df_train$Exercise_Hours, breaks = c(-1, 1, 3, 6, 20), labels = c("Very Low", "Low", "Moderate", "High"))
exercise_dummies <- model.matrix(~ Exercise_Level, data = df_train) |>as.data.frame()
exercise_dummies <- exercise_dummies[, !names(exercise_dummies) %in% "(Intercept)"]
df_train <- cbind(df_train[, !names(df_train) %in% "Exercise_Level"], exercise_dummies)

```

At this step for python version from Machine Learning 1 course we've taken code for downcasting our dataframe. The function downcast_dataframe() is used to reduce the memory usage of a DataFrame by converting each column to the smallest possible data type that can still hold all its values. Downcasting can reduce memory usage by 50–90%. 

In **R version** we decided to omit this function - R primarily operates with just two numeric types (integer and double), and more granular downcasting is not easily supported and would require additional packages. Taking into consideration our small dataset and very little potential memory savings the change would be neglible. 

```{r ensuring test set}
# Apply same transformations to test set

#drop location
df_test <- df_test[, !names(df_test) %in% "Location"]

#one-hot
test_dummies <- model.matrix(~ Gender + School_Grade + Phone_Usage_Purpose, data = df_test) |> as.data.frame()
test_dummies <- test_dummies[, !names(test_dummies) %in% "(Intercept)"]
df_test <- cbind(df_test[, !names(df_test) %in% c("Gender", "School_Grade", "Phone_Usage_Purpose")], test_dummies)

#new features
df_test$Total_Phone_Time <- df_test$Time_on_Social_Media + df_test$Time_on_Gaming + df_test$Time_on_Education
df_test$Checks_per_Hour <- df_test$Phone_Checks_Per_Day / (df_test$Daily_Usage_Hours + 1e-12)
df_test$Night_Usage_Ratio <- df_test$Screen_Time_Before_Bed / (df_test$Daily_Usage_Hours + 1e-12)
df_test$Digital_Life_Balance <- (df_test$Exercise_Hours + df_test$Sleep_Hours) / (df_test$Daily_Usage_Hours + 1e-12)

df_test$Entertainment_to_Education_Ratio <- (df_test$Time_on_Social_Media + df_test$Time_on_Gaming) /     (df_test$Time_on_Education + 1e-3)

df_test$Exercise_Level <- cut( df_test$Exercise_Hours, breaks = c(-1, 1, 3, 6, 20), labels = c("Very Low", "Low", "Moderate", "High"))
exercise_dummies_test <- model.matrix(~ Exercise_Level, data = df_test) |> as.data.frame()
exercise_dummies_test <- exercise_dummies_test[, !names(exercise_dummies_test) %in% "(Intercept)"]
df_test <- cbind(df_test[, !names(df_test) %in% "Exercise_Level"], exercise_dummies_test)

```

```{r contains}
setdiff(names(df_train), names(df_test))
setdiff(names(df_test), names(df_train))
```
